Review of Assigned Readings

### 2018-01-04 paper/paper.tex
Update paper.tex

%************************** Title Page **************************   
\begin{titlepage}
	\begin{figure}
	\centering
	\includegraphics[scale=0.32]{logohsg}
	\end{figure}
\centering
{\scshape\large School of Management, Economics, Law, Social Sciences and International Affairs \par}
\vspace{2.0cm}
{\huge\bfseries The effect of Twitter activity on Bitcoin price fluctuation  \par}
\vspace{2.0cm}
{\scshape\Large Software Engineering for Economists \\(7,610,1.00) \par}
\vspace{2.0cm}
{\itshape\large Alen Stepic - 11-475-258 \\Dimitrios Koumnakes - 10-613-370 \\Joël Sonderegger - 11-495-488 \\Severin Kranz - 13-606-355 \\Chi Xu - XX-XXX-XXX \par}
	\begin{spacing}{1}
	\vspace{1.2cm}
	{Fall Term 2017 \par}
	\vspace{1.2cm}
	Supervisor:\\
	{Prof. Dr. Philipp Zahn\\ FGN HSG\\ Varnbüelstrasse 19\\ 9000 St. Gallen \par}
	\end{spacing}
\vfill
{\large \today\par}
\end{titlepage}

>>>>

%************************** Title Page **************************   
\begin{titlepage}
	\begin{figure}
	\centering
	\includegraphics[scale=0.32]{logohsg}
	\end{figure}
\centering
{\scshape\large School of Management, Economics, Law, Social Sciences and International Affairs \par}
\vspace{2.0cm}
{\huge\bfseries The effect of Twitter activity on Bitcoin price fluctuation  \par}
\vspace{2.0cm}
{\scshape\Large Software Engineering for Economists \\(7,610,1.00) \par}
\vspace{2.0cm}
{\itshape\large Alen Stepic - 11-475-258 \\Dimitrios Koumnakes - 10-613-370 \\Joël Sonderegger - 11-495-488 \\Severin Kranz - 13-606-355 \\Chi Xu - 16-300-915 \par}
	\begin{spacing}{1}
	\vspace{1.2cm}
	{Fall Term 2017 \par}
	\vspace{1.2cm}
	Supervisor:\\
	{Prof. Dr. Philipp Zahn\\ FGN HSG\\ Varnbüelstrasse 19\\ 9000 St. Gallen \par}
	\end{spacing}
\vfill
{\large \today\par}
\end{titlepage}
